---
title: "COVID-19 Cases/Vaccinations Examination"
description: |
  An Examination of COVID-19 data in various countries and continents. 
site: distill::distill_website
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(plotly)
library(ggthemes)
```

```{r include = FALSE}
clean_cases_data <- read_csv("owid-covid-data.csv") %>% 
  select(location, date, new_cases_smoothed, new_cases_smoothed_per_million) %>% 
  filter(location == c("China", "Canada", "United States", "United Kingdom")) %>% 
  mutate(new_cases_percentage = new_cases_smoothed_per_million / 1000000) %>% 
  drop_na()
clean_vaccinations_data <- read_csv("owid-covid-data.csv") %>% 
  select(location, date, new_vaccinations_smoothed_per_million, new_vaccinations_smoothed) %>% 
  filter(location == c("China", "Canada", "United States", "United Kingdom")) %>% 
  mutate(new_vaccinations_percentage = new_vaccinations_smoothed_per_million / 1000000) %>% 
  drop_na()

```

## Visualization
Graphs below visually demonstrate the recent data about case and vaccination situations in China, Canada, United States, and United Kingdom.

### Weekly Cases
The graph below demonstrates current data of weekly COVID-19 cases in China, Canada, United States, and United Kingdom starting from February 2020.

```{r, echo = FALSE}
clean_cases_data %>% 
  ggplot() +
  geom_line(aes(x = date, y = new_cases_percentage, color = location)) +
  facet_wrap(~location) +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(title = "Weekly COVID-19 Cases in Four Countries",
       subtitle = "Number of cases in China is siginificantly lower than others",
       x = "Date",
       y = "Weekly Cases Percentage",
       color = "Country",
       caption = "Source: Our World in Data")
```

### Analysis
According to the graph, China did significantly better than the other countries on controlling the spread of virus because the line representing China's data is constantly at a level that is around 0%. An interesting point to note is that Canada, United Kingdom, and United states all have a peak during January 2021, and it could represent that virus or social communication is most active during that time period.

### Weekly Vaccinations
The graph below demonstrates current data of weekly vaccinations in China, Canada, United States, and United Kingdom starting from January 2021.

```{r, echo = FALSE}
vaccinations_graph <- clean_vaccinations_data %>% 
  ggplot(aes(x = date, y = new_vaccinations_percentage, color = location,
             text = paste("Date:", date, "\n", "Number of Vaccinations", new_vaccinations_smoothed)))+
  geom_point() +
  facet_wrap(~location) +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(title = "Weekly COVID-19 Vaccinations in Four Countries",
        subtitle = "All countries made a significant progress on vaccination",
        x = "Date",
        y = "Weekly Vaccinations Percentage
       ",
       color = "Country",
       caption = "Source: Our World in Data") 
  
ggplotly(vaccinations_graph, tooltip = "text")
```
<aside>
Source: Our World in Data
</aside>

### Analysis
According to the graph, China and Canada have a constantly positive trend of vaccination progress, whereas United Kingdom fluctuates frequently starting from February. The trend in United States is dramatic since the number of vaccination grew consistently before mid-April, but it began to drop intensely after that. 
